---
title: "Marriages in Toronto from 2015 - 2020"
author: 
  - Yunkai Gu
thanks: "Code and data are available at: LINK."
date: 19 September 2024
date-format: long
abstract: "This paper conducts brief analysis on the marriages in Toronto from 2015 - 2020 mainly using data from opendatatoronto."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR, @opendatatoronto, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of marriage (@fig-marriage), from @opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

The number of marriage licenses appears to have density of points under 500 before 2020. However, there is also points randomly distributed around 500-100 during the five years.





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References